\documentclass[A4]{article}

%opening
\title{“How Kikoni residents like to eat their “rolexes”, with or without tomatoes.”}
\author{By Kyobweine Bikangaga Prisca
	216002579
	16/U/6489/PS
}

\begin{document}

\maketitle

\begin{abstract}
A “rolex” is a common delicacy hailing from Uganda, that is basically made by rolling fried eggs inside “chapatti(s)”, and desired addition ingredients such as tomatoes, onions, cabbage, green pepper and any other complementary ingredients as desired by the customer.
\end{abstract}

\section{Introduction}
The main purpose of this research was to figure out which ingredients the customers in Kikoni prefer to be included in their rolexes. The current theory is that most customers prefer to include tomatoes in their rolex.
\section{Methods}
For the first two days of my research, I interviewed gentlemen who prepare Rolexes, about what they think are the most preferred ingredients. I then proceeded to ask ten random people how best they like to have their Rolexes.
For the next three days, I then sat in sight of three different rolex stands, spending thirty minutes at each one, trying to observe which ingredients customers opted for and which ones were least ordered.
\section{Results}
During the interviews, I discovered that an overwhelming majority preferred to include tomatoes in their rolex. One person out of the ten people preferred to have their rolex without tomatoes. The response from the gentlemen who prepare the Rolexes also supported the above fact, as they said they spend a lot more on tomatoes since almost every customer they have, asks for tomatoes in their rolex.
My observations of the three stands helped me realize that generally for every fifteen people who want tomatoes in their rolex, twelve of them, which is eighty percent, ordered for raw tomatoes, while the minority opted to have their tomatoes fried within the egg. 
\section{Conclusion}
According to the results, regardless of whether the customer prefers raw tomatoes or those fried within the egg, it confirms the theory that most customers indeed like to have tomatoes included in their rolex.
\
\end{document}
